---
title: "mtcars Plotly"
author: "Willianto Asalim"
date: "28/07/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## mtcars Plotly Information

This is a 5 web page presentation using R Markdown that features a plot created with Plotly. It contains interactive tables where you can move the columns around and an interactive plot of mtcars data with fitted loess line (mpg~disp).

In the interactive plot:

- You can view the car info by hovering over the point.
- You can click on the legend to show/hide the data
- You can zoom into the data by using your mouse and highlight the selected area (double click to zoom out).


## Interactive mtcars data table

```{r carsTable, warning=FALSE, message=FALSE}
library(plotly)

fig <- plot_ly(
  type = 'table',
  header = list(
    values = c("<b>Cars</b>", names(mtcars)),
  align = c('left', rep('center', ncol(mtcars))),
  line = list(width = 1, color = 'black'),
  fill = list(color = 'rgb(235, 100, 230)'),
  font = list(family = "Arial", size = 14, color = "white")
  ),
  cells = list(
    values = rbind(
      rownames(mtcars), 
      t(as.matrix(unname(mtcars)))
    ),
    align = c('left', rep('center', ncol(mtcars))),
    line = list(color = "black", width = 1),
    fill = list(color = c('rgb(235, 193, 238)', 'rgba(228, 222, 249, 0.65)')),
    font = list(family = "Arial", size = 12, color = c("black"))
  ))

fig
```

## Interactive mtcars Plot

```{r carsPlot, warning=FALSE, message=FALSE}
figPlot <- plot_ly(mtcars, x = ~disp, color = ~factor(cyl))
figPlot <- figPlot %>% add_markers(y = ~mpg, text = rownames(mtcars), showlegend = TRUE)
figPlot <- figPlot %>% add_lines(y = ~fitted(loess(mpg ~ disp)),
            line = list(color = '#07A4B5'),
            name = "Loess Smoother", showlegend = TRUE)
figPlot <- figPlot %>% layout(xaxis = list(title = 'Displacement (cu.in.)'),
         yaxis = list(title = 'Miles/(US) gallon'),
         legend = list(x = 0.80, y = 0.90))

figPlot
```

## Thank you!

To view the code plese go to this website: https://github.com/asalimw/mtcarsPlotly
